Addition and removal energies of circular quantum dots

### 2017-04-27 Manuscript/paper.tex
Update Manuscript/paper.tex
Update fit data for fit_count=5

The White generator is explicitly constructed the following way \cite{PhysRevLett.106.222502,White:cond-mat0201346}.  Let
\begin{align*}
\hat{\eta}^{\text{Wh}} &\equiv \hat{\eta}' - \hat{\eta}'{}^\dagger
\end{align*}
where
\begin{align*}
\eta^{\prime [1]}_{a, i} &\equiv \frac{\bar{n}_a n_i H^{[1]}_{a, i}}{\tilde{\Delta}^{[1]}_{a, i}} &
\eta^{\prime [2]}_{a, b, i, j} &\equiv \frac{\bar{n}_a \bar{n}_b n_i n_j H^{[2]}_{a, b, i, j}}{\tilde{\Delta}^{[2]}_{a, b, i, j}}
\end{align*}
and the Epstein--Nesbet denominators $\tilde{\Delta}$ are defined as
\begin{align}
\tilde{\Delta}^{[1]}_{a, i} &\equiv \Delta_{\{a\}, \{i\}} - H^{[2]}_{a, i, a, i} \notag \\
\tilde{\Delta}^{[2]}_{a, b, i, j} &\equiv \Delta_{\{a, b\}, \{i, j\}} + w_{a, b, i, j} \notag \\
\Delta^{[2]}_{P_1, P_2} &\equiv \sum_{p_1 \in P_1} H^{[1]}_{p_1, p_1} - \sum_{p_2 \in P_2} H^{[1]}_{p_2, p_2} \label{eq:moellerplessetdenominator} \\
w_{a, b, i, j}
  &\equiv H^{[2]}_{a, b, a, b} - H^{[2]}_{a, i, a, i} - H^{[2]}_{b, i, b, i} \notag \\
  &\qquad + H^{[2]}_{i, j, i, j} - H^{[2]}_{a, j, a, j} - H^{[2]}_{b, j, b, j} \notag
\end{align}
Some literature use the M\o eller--Plesset denominators $\Delta$ instead, leading to a slightly different variant of the White generator.

@@

Not all cases are solvable with our selection many-body methods.  Low frequency systems are particularly strenuous for these many-body methods due to their strong correlations, leading to equations that are difficult and expensive to solve numerically.  Cases where the methods required more than our allocated times to arrive at a result are marked ``n.c.'' (``no convergence'').  For the extrapolations in Section \ref{subsec:extrapolation}, some fits did not converge to a sensible result (i.e.\ nonnegative exponents) -- these are marked ``n.f.'' (``no fit'').  Other cases where results are simply unavailable for technical or logistic reasons are left blank in the tables.

>>>>

The White generator is explicitly constructed the following way \cite{PhysRevLett.106.222502,White:cond-mat0201346}.  Let
\begin{align*}
\hat{\eta}^{\text{Wh}} &\equiv \hat{\eta}' - \hat{\eta}'{}^\dagger
\end{align*}
where
\begin{align*}
\eta^{\prime [1]}_{a, i} &\equiv \frac{\bar{n}_a n_i H^{[1]}_{a, i}}{\tilde{\Delta}^{[1]}_{a, i}} &
\eta^{\prime [2]}_{a, b, i, j} &\equiv \frac{\bar{n}_a \bar{n}_b n_i n_j H^{[2]}_{a, b, i, j}}{\tilde{\Delta}^{[2]}_{a, b, i, j}}
\end{align*}
and the Epstein--Nesbet denominators $\tilde{\Delta}$ are defined as
\begin{align}
\tilde{\Delta}^{[1]}_{a, i} &\equiv \Delta_{\{a\}, \{i\}} - H^{[2]}_{a, i, a, i} \notag \\
\tilde{\Delta}^{[2]}_{a, b, i, j} &\equiv \Delta_{\{a, b\}, \{i, j\}} + w_{a, b, i, j} \notag \\
\Delta^{[2]}_{P_1, P_2} &\equiv \sum_{p_1 \in P_1} H^{[1]}_{p_1, p_1} - \sum_{p_2 \in P_2} H^{[1]}_{p_2, p_2} \label{eq:moellerplessetdenominator} \\
w_{a, b, i, j}
  &\equiv H^{[2]}_{a, b, a, b} - H^{[2]}_{a, i, a, i} - H^{[2]}_{b, i, b, i} \notag \\
  &\qquad + H^{[2]}_{i, j, i, j} - H^{[2]}_{a, j, a, j} - H^{[2]}_{b, j, b, j} \notag
\end{align}
Some literature use the M\o ller--Plesset denominators $\Delta$ instead, leading to a slightly different variant of the White generator.

@@

Not all cases are solvable with our selection many-body methods.  Low frequency systems are particularly strenuous for these many-body methods due to their strong correlations, leading to equations that are difficult and expensive to solve numerically.  Cases where the methods required more than our allocated time to arrive at a result are marked ``n.c.'' (``no convergence'').  For the extrapolations in Section \ref{subsec:extrapolation}, some fits did not converge to a sensible result (i.e.\ nonnegative exponents) -- these are marked ``n.f.'' (``no fit'').  Other cases where results are simply unavailable for technical or logistic reasons are left blank in the tables.
